\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Prajna Kandarpa}
I have more than 3 years of experience in the fields of software development,
hardware development and web development. I have previously designed and
developed Minimum Viable Products (MVPs) during my stints at startups with
minimal supervision and tons of collaboration with teammates. I am able to bring
ideas for products to fruition after careful determination of a client's needs.
Very fast learner with an intuitive grasp of architectural patterns utilized in
modern IT systems design

\section{Education}

\begin{yearlist}

\item[Bachelor of Applied Science in Mechatronics Engineering]{2010 -- '16}
  {University of Waterloo, Canada}
  {This program consists of 8 study terms and 6 internships, each being 4 months
    in length}
\end{yearlist}
\section{Work experience}

\begin{eventlist}

\item {Jun '16 - Jan '17}
  {Research Associate, Real-time Embedded Systems Lab}
  {University of Waterloo, Canada}

  Made responsive data visuals for the web to pinpoint defects in automotive and
  aeronautical systems. Investigated and created machine learning models using
  techniques including auto-encoders, neural nets, Markov Models and ensembles
  of networks for prognostics and failure detection.

\item{Jul '15 - Dec '15, Jun '16 - Dec '16}
  {Full Stack Engineer}
  {Acerta Analytics, Waterloo, Canada}

  Investigated and developed techniques for unsupervised and supervised time
  series anomaly detection in critical risk systems - automotive and
  aeronautical vehicles. Helped design our data processing infrastructure. Used
  Amazon Web Services to deploy client-facing products. Designed wireframes and
  created MVPs after deliberation with customers for their data analytics needs.

\item{Mar '15 - Jun '15}
  {Full Stack Engineer}
  {Ubiq, Inc., Kitchener, Canada}

  Developed a low latency desktop streaming module for enterprise meeting rooms
  in C and integrated it into our OS X application. Implemented communication
  APIs in Python and Objective C. Worked as part of a four member engineering
  team that spent long hours working with complex software libraries for
  multimedia processing.

\item{May '14 - Dec '14}
  {Diagnostics Engineer}
  {Arista Networks, Santa Clara, USA}

  Assisted the hardware team, developed software based automation of PCB
  verification and manufacturing test system verification as part of the
  Diagnostics team. Used system comm. protocols like SMBus, I2C and JTAG to
  facilitate comms and automated multi-level tests in the PCB. Added features to
  manufacturing test automation infrastructure, written using Python Django.

\item{Sep '13 -- Dec '13}
  {Software Developer}
  {Trapeze Group, Mississauga, Canada}

  % Worked on multiple web applications that relate product development history
  % with code repository statistics. Used Subversion Java API, Java Servlets and
  % the Grails application framework. Improved page load times, database
  % performance and cleaned up internal APIs.


\item{Jan '13 -- Apr '13}
  {Web Platform Engineer}
  {Morgan Stanley Financial Services, Montreal, Canada}

  % Developed document lifecycle workflows for TWiki, a wiki application used as a
  % knowledge base. Gained in-depth knowledge of wiki applications' network
  % configuration, load balancing techniques and site mirroring. Wrote plugins in
  % Perl to implement Document Review workflows based on LDAP User, Group ACLs.
  % Collaborated with team members from New York, Shanghai and Tokyo during an
  % iterative design process.

\end{eventlist}



\personal
[prajis.me]
{\#203, Lakshmi Residency, Kothasalipeta, Visakhapatnam, India - 530003}
{+91 85000 06699}
{spspkand@uwaterloo.ca}
\vspace{0.4cm}

\section{Soft Skills}

\begin{factlist}
\item{Communication} {Excellent spoken, written English. Experience with technical and
    business communication prose. Moderate experience with public speaking}
\item{Teams} {Worked in teams of sizes ranging from 2 - 10. Very easy to get
    along with and a strong team player that can be trusted upon to deliver project
    milestones}
\end{factlist}
\section{Technical Skills}

\begin{factlist}
\item{LANGUAGES}
  {Javascript, R, Go, Typescript, Python, Objective-C, C, Java, MATLAB}

\item{TOOLS}
  {emacs, git, docker, grunt, LaTEX, Xcode, PostgreSQL, MySQL}

\item{PLATFORMS}
  {OS X, Linux, Windows, ArduCopter}

\item{FRAMEWORKS}
  {Scikit-learn, AngularJS, NodeJS, D3.js, FFmpeg, SailsJS, Django, Bootstrap}

\item{DESIGN}
  {HTML, CSS, Wireframes}


\end{factlist}

\section{Projects}

\begin{yearlist}

\item{'16}
  {Talon \href{http://talonco.github.io}{talonco.github.io}}
  {Our 4 person team built an add-on kit for delivery vehicles that enables drone deliveries with integrations for existing warehouse management systems.The kit provides automated package loading and drone takeoff, landing}

\end{yearlist}

\section{Courses}

\begin{yearlist}

\item{'16} {Computational Neuroscience} {Study the neurobiological systems that
    make up the brain and central nervous system and design software
    equivalents.}

\item{'16} {Machine Intelligence} {A study of artificial intelligence techniques
    such as Bayesian frameworks, fuzzy logic, decision trees, neural networks
    and reinforcement learning}

\item{'15}
  {Image Processing}
  {A study of human visual system, frequency domain enhancement and image color processing}
\item{'12} {Operating Systems} {Intro to memory, resource and process
    management, interrupt handling, concurrent programming, file systems.}



\end{yearlist}

% \section{Communication skills}

% \begin{factlist}
% \item{Italian}{Native speaker}
% \item{English}{Oral: fair -- Written: good}
% \item{Spanish}{Oral: good}
% \end{factlist}

\end{document}
